GrapeCPNet: A deep learning integration for grape completion and phenotyping in 3D

### 2025-01-06 main.tex
update section cite

\subsubsection{3D reconstruction of grape}

@@

\subsection{Berry Instance Segmentation}

@@

In order to train and validate SoftGroup, each berry and stem in the bunch point cloud obtained in
% todo
Section 2.1.2 was labeled at the instance-level (Fig.~\ref{fig:raw11}). 
This paper collected and labeled 8 bunches for each of the four species (total 32 bunches). 
In the sample division, 5 grape bunches of each species (total 20) are randomly selected and used as training samples, the remaining 12 bunches are used for validation.

@@

The point cloud completion network often requires the incomplete-complete data pairs of the same object to build a mapping relationship. 
In this paper, the complete grapes were obtained by single berry reconstruction 
%todo
(Section 2.1.2) and were used as ground truth, while the incomplete grapes were cut from the complete grapes following characteristic of occlusion and were used as training inputs. 
This data pair generation strategy saved huge amounts of data annotation. The common incomplete characteristics of the berry are shown in Figure~\ref{fig:raw4}.
Based on the incomplete characteristics, we developed a cutting method for the complete berry point cloud to generate the incomplete berry point cloud.

@@

For the model inference validation, among 12 testing grape bunches of the berry instance segmentation model 
%todo
(Section 2.2), each grape species was randomly selected one bunch (total 4 bunches). 
For each bunch, 27 berries are randomly selected, and finally obtain a total of 108 incomplete berries as the input data for completion network inference validation. 
By checking the labels of these berries, the corresponding single complete berry reconstruction results %todo
(Section 2.1.2 \& Fig.~\ref{fig:raw9}c) were used as ground truth.

@@

In order to validate the accuracy of extracted morphological traits, those 12 validation bunches in %todo
Section 2.2 were continuously used after instance berry segmentation and berry completion. 
The radius and volume of the 108 samples are calculated. 
For ground truth measurement, instead of using manual measurement, which has multiple artificial errors in obtaining the true values of actual radius and volume. 
This paper used the correspond individual complete berry as the ground truth and applied the same method for the radius and volume calculations.

@@

\subsubsection{Berry instance segmentation}

In this paper, we use the format of SoftGroup \citep{vu_softgroup_2022} that is consistent with the S3DIS dataset \citep{armeni_3d_2016} and use the average precision AP \citep{vu_softgroup_2022} as the evaluation metric for berry instance segmentation. In the threshold setting, the average of the APs with selected the IoU (Intersection over Union) from 50\% to 95\% in steps of 5\% is noted as AP@50:5:95.

@@

\subsubsection{Phenotypic traits calculation}

In order to evaluate the efficiency of the number of berry statistics and the calculation of berry radius and volume, the MAE (Mean Absolute Error) and the coefficient of determination $R^2$ (R-Square) are used to calculate the error between the prediction value and the true value of the sample.

@@

Bunch point cloud segmentation is mainly realized based on SoftGroup, a point cloud segmentation network. 
This paper calculates the segmentation results for the berry instances and stem instances using the dataset introduced in 
%todo
Section 2.2 and the evaluation metrics in Section 2.5.1, as shown in Table~\ref{tbl:3}.

@@

Based on the method in this paper, the bunch point cloud is used as input, and the acquired 3D phenotypic parameters are the final output, which mainly contains two parts: the bunch-level phenotypic parameters and the berry-level phenotypic parameters.
In this paper, experiments are conducted to calculate berry radius and volume with the dataset in the evaluation metrics in 
%todo
Section 2.5.3.
The radius parameters are calculated by fitting the berry to the surface of an ellipsoid, as shown in Figure~\ref{fig:raw16}.

@@

Three lengths of the radius of the berry can be obtained by fitting the predicted point cloud of the complete berry shell to the surface of an ellipsoid. 
Meanwhile, the point cloud data acquisition method in 
%todo
Section 2.1.2 can translate the scale of the point cloud space to the real world, so as to get the real radius length of the berry.
Because of the large difference between the ratio of the long and short axis of different species, this paper conducted experiments on the calculation of the axis length of four species respectively, as shown in Figure~\ref{fig:raw17}.

>>>>

\subsubsection{3D reconstruction of grape}
\label{sec:212}

@@

\subsection{Berry Instance Segmentation}
\label{sec:22}

@@

In order to train and validate SoftGroup, each berry and stem in the bunch point cloud obtained in Section~\ref{sec:212} was labeled at the instance-level (Fig.~\ref{fig:raw11}). 
This paper collected and labeled 8 bunches for each of the four species (total 32 bunches). 
In the sample division, 5 grape bunches of each species (total 20) are randomly selected and used as training samples, the remaining 12 bunches are used for validation.

@@

The point cloud completion network often requires the incomplete-complete data pairs of the same object to build a mapping relationship. 
In this paper, the complete grapes were obtained by single berry reconstruction (Section~\ref{sec:212}) and were used as ground truth, while the incomplete grapes were cut from the complete grapes following characteristic of occlusion and were used as training inputs. 
This data pair generation strategy saved huge amounts of data annotation. The common incomplete characteristics of the berry are shown in Figure~\ref{fig:raw4}.
Based on the incomplete characteristics, we developed a cutting method for the complete berry point cloud to generate the incomplete berry point cloud.

@@

For the model inference validation, among 12 testing grape bunches of the berry instance segmentation model (Section~\ref{sec:22}), each grape species was randomly selected one bunch (total 4 bunches). 
For each bunch, 27 berries are randomly selected, and finally obtain a total of 108 incomplete berries as the input data for completion network inference validation. 
By checking the labels of these berries, the corresponding single complete berry reconstruction results (Section~\ref{sec:212} \& Fig.~\ref{fig:raw9}c) were used as ground truth.

@@

In order to validate the accuracy of extracted morphological traits, those 12 validation bunches in Section~\ref{sec:22} were continuously used after instance berry segmentation and berry completion. 
The radius and volume of the 108 samples are calculated. 
For ground truth measurement, instead of using manual measurement, which has multiple artificial errors in obtaining the true values of actual radius and volume. 
This paper used the correspond individual complete berry as the ground truth and applied the same method for the radius and volume calculations.

@@

\subsubsection{Berry instance segmentation}
\label{sec:251}
In this paper, we use the format of SoftGroup \citep{vu_softgroup_2022} that is consistent with the S3DIS dataset \citep{armeni_3d_2016} and use the average precision AP \citep{vu_softgroup_2022} as the evaluation metric for berry instance segmentation. In the threshold setting, the average of the APs with selected the IoU (Intersection over Union) from 50\% to 95\% in steps of 5\% is noted as AP@50:5:95.

@@

\subsubsection{Phenotypic traits calculation}
\label{sec:253}
In order to evaluate the efficiency of the number of berry statistics and the calculation of berry radius and volume, the MAE (Mean Absolute Error) and the coefficient of determination $R^2$ (R-Square) are used to calculate the error between the prediction value and the true value of the sample.

@@

Bunch point cloud segmentation is mainly realized based on SoftGroup, a point cloud segmentation network. 
This paper calculates the segmentation results for the berry instances and stem instances using the dataset introduced in Section~\ref{sec:22} and the evaluation metrics in Section~\ref{sec:251}, as shown in Table~\ref{tbl:3}.

@@

Based on the method in this paper, the bunch point cloud is used as input, and the acquired 3D phenotypic parameters are the final output, which mainly contains two parts: the bunch-level phenotypic parameters and the berry-level phenotypic parameters.
In this paper, experiments are conducted to calculate berry radius and volume with the dataset in the evaluation metrics in Section~\ref{sec:253}.
The radius parameters are calculated by fitting the berry to the surface of an ellipsoid, as shown in Figure~\ref{fig:raw16}.

@@

Three lengths of the radius of the berry can be obtained by fitting the predicted point cloud of the complete berry shell to the surface of an ellipsoid. 
Meanwhile, the point cloud data acquisition method in Section~\ref{sec:212} can translate the scale of the point cloud space to the real world, so as to get the real radius length of the berry.
Because of the large difference between the ratio of the long and short axis of different species, this paper conducted experiments on the calculation of the axis length of four species respectively, as shown in Figure~\ref{fig:raw17}.
